Joint Power Allocation and Network Slicing In an End to End O-RAN System

### 2019-10-20 Latex/tex/pr.tex
finish fig2 and 3

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

@@

 \begin{table}[H]

@@

 \begin{table}[H]

@@

When we have two DCs, proposed method and optimal method have approximately same ratio of admitted slices. But by increasing the number of DCs to five, performance of proposed method reduced.

@@

    \includegraphics[width=\linewidth]{f1}

@@

\begin{figure}[H]
  \centering
    \includegraphics[width=\linewidth]{f2}
  \caption{Normalized resource consumption vs. Number of slices}
  \label{fig:f2}
\end{figure} 
\bibliographystyle{ieeetr}
\bibliography{ref}
\end{document}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{mathtools} 
\usepackage{stackengine}
\def\delequal{\mathrel{\ensurestackMath{\stackon[1pt]{=}{\scriptstyle\Delta}}}}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{amsmath,epsfig,cite,amsfonts,amssymb,psfrag,subfig}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{amsthm}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\allowdisplaybreaks
\newtheorem{remark}{Remark}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{corollary}{Corollary}

@@

 \begin{table}

@@

When we have two DCs, proposed method and optimal method have approximately same ratio of admitted slices. But by increasing the number of DCs to five, performance of proposed method reduced. Using five DCs, the difference between 
proposed method and optimal method in worst case (44 slices) is about $23$ percentage. 
 \begin{table}

@@

@@

    \includegraphics[width=\linewidth]{f11}

@@

In Fig. \ref{fig:f2}, the normalized resource consumption is depicted due to the number of slices (the parameters for simulation listed in table \ref{table:1} and \ref{table:2}). In this simulation, it is assumed that number of DCs is completely enough to cover all slices. The optimality of placement of DCs to slices is measured. It is shown that how much resources of active DCs are not used. For ten slices, the difference between optimal solution and proposed solution is about $15$ percent. 
    \includegraphics[width=\linewidth]{fig2_last}
  \caption{Normalized Resource Consumption vs. Number of Slices}
  \label{fig:f2}
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}
